\documentclass{TaylorTurnerResume2023}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\begin{document}

%	TITLE NAME
\namesection{Taylor}{Turner}{Software Engineer}{\contactline{\href{mailto:resume.tturner@gmail.com}{resume.tturner@gmail.com}}
{\href{tel:+618-402-4677}{618-402-4677}}
{\href{https://www.linkedin.com/in/ifTaylorthenHire}{ifTaylorthenHire}}
{\href{https://github.com/ifTaylor}{ifTaylor}}
{\href{https://ifTaylor.com}{ifTaylor.com}}}

%	COLUMN ONE
\begin{minipage}[t]{0.7\textwidth} 

%	EXPERIENCE
\section{Experience}
\runsubsection{Bastian Solutions}
\descript{| Software Engineer}
\location{1 year | September 2022 – Current | Maryland Heights, MO}
\vspace{\topsep}
\begin{tightemize}
\sectionsep
\item Developed software for manufacturing applications and interfacing automation controllers, robots, and vision systems.
\sectionsep
\item Migrated a palletization application from WinForms to .NET Core and Next.js/React frameworks.
\begin{tabular}{ p{6cm} l }
\textbullet\ Reactive pallet pattern editing & \textbullet\ Real-time peripheral device interrupts \\
\textbullet\ Entity Framework Core relational database & \textbullet\ REST API methods \\
\textbullet\ Utility Patented
\end{tabular}
\sectionsep
\item Enhanced a robot picking application to bridge device communication using Python.
\begin{tabular}{ p{6cm} l }
\textbullet\ Vision system communication with gRPC & \textbullet\ Automation Control with OPC UA and Pylogix \\
\textbullet\ Serial buffering to robots & \textbullet\ Statistical data analysis of picking performance \\
\textbullet\ Vision A.I. annotation
\end{tabular}
\sectionsep
\item Improved interoperability among peripheral devices and automated statistical data collection for tracking performance.
\sectionsep
\item Transitioned products from R\&D to manufacturing, focusing on continuous improvement in integration testing and product statistics.  
\end{tightemize}
\sectionsep
\sectionsep

\runsubsection{Beckwood Press}
\descript{| Electrical Controls Engineer }
\location{6 years | October 2016 – September 2022 | Fenton, MO}
\begin{tightemize}
\sectionsep
\item Designed electrical systems for custom hydraulic and servo presses.
\sectionsep
\item Programmed controls applications using automation controllers. 
\begin{tabular}{ p{6cm} l }
\textbullet\ Procedural logic for discrete systems & \textbullet\ Operator U.I. ergonomics \\
\textbullet\ Sensor filtering and linearization & \textbullet\ Machine parameter database \\
\textbullet\ Closed-loop motion control
\end{tabular}
\sectionsep
\item Facilitated team collaboration to understand and prioritize low-level solutions. Our team grew design processes for accelerated development and integration.
\sectionsep
\item Led product performance publications. Extensive data collection, white-papers and marketing strategy showcased product performance and competitiveness within the marketplace.
\end{tightemize}
\sectionsep
\sectionsep

\runsubsection{EPIC Inc.}
\descript{| Electrical Controls Technician }
\location{2 years | December 2014 – October 2016 | St. Louis, MO}
\begin{tightemize}
\sectionsep
\item Oversaw the assembly and design of electrical panels and machine wiring
\begin{tabular}{ l l l }
\textbullet\ Pilot plants & \textbullet\ Vision systems & \textbullet\ Custom Machines
\end{tabular}
\sectionsep
\item Implemented designs that conformed to sanitary/wash-down, Class I Division I, and National Electric Code requirements.              
\sectionsep
\textbullet\ The multidisciplinary nature of these products gave the opportunity to be cross-trained in mechanical and process design.
\end{tightemize}
\sectionsep
\sectionsep

\runsubsection{Pristine STL}
\descript{| Chief Technology Officer (Techno Dad) }
\location{3 years | December 2020 – Present | St. Louis, MO}
\begin{tightemize}
\sectionsep
\item Pridefully provide technology solutions for our family business.
\sectionsep
\item Created and maintain the development and promotion of Pristine's website \uline{\href{https://pristinestl.com}{pristinestl.com}}
\sectionsep
\item Deploy calendar and schedule solutions for the owner and crews.            
\end{tightemize}
\sectionsep

%	COLUMN TWO
\end{minipage} 
\hfill
\begin{minipage}[t]{0.275\textwidth} 

% SKILLS
\section{Skills}

\subsection{Programming Languages}
\location{Proficient:}
  \textbullet{} C\#
  \textbullet{} Python
  \textbullet{} SQL Server
  \textbullet{} TypeScript
  \textbullet{} HTML
  \textbullet{} JavaScript
  \textbullet{} Automation Controllers
  
\location{Familiar:}
  \textbullet{} C/C++
  \textbullet{} Visual Basic
  \textbullet{} Blazor \\
  \textbullet{} PowerShell
  \textbullet{} \LaTeX
\sectionsep
\subsection{Frameworks and Libraries}
  \textbullet{} ASP.NET Core
  \textbullet{} Entity Framework \\
  \textbullet{} Flask
  \textbullet{} gRPC
  \textbullet{} Node.js
  \textbullet{} React.js \\
  \textbullet{} Next.js
  \textbullet{} ClxDriver
  \textbullet{} Interop.FRRobot
\sectionsep
\subsection{Development Tools and \\ Environments}
  \textbullet{} Visual Studio
  \textbullet{} VS Code
  \textbullet{} Git \\
  \textbullet{} Postman
  \textbullet{} Swagger
  \textbullet{} Vercel
  \textbullet{} GitHub \\
  \textbullet{} Azure
  \textbullet{} TexMaker
\sectionsep
\subsection{Methodologies and Concepts}
  \textbullet{} Agile/Sprint
  \textbullet{} Object-Oriented Programming (OOP)
  \textbullet{} Failure Modes and Effects Analysis (FMEA)
  \textbullet{} UL 508A \\
  \textbullet{} SCADA
  \textbullet{} Project Management
\sectionsep
\sectionsep
%	EDUCATION
\section{Education} 
\subsection{Ranken Technical College}
\descript{Associate's Degree: \\ Electrical Control Systems}
\location{December 2014 | St. Louis, MO}

%	Volunteer
\section{Volunteer} 
{\textbf{Offensive/Defensive Line Coach},\\
Titans of Troy, IL}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{Coursework}

% \subsection{Graduate}
% Graduate Algorithms \textbullet{}\\ 
% Advanced Computer Architecture \textbullet{}\\ 
% Operating Systems \textbullet{}\\ 
% Artificial Intelligence \textbullet{}\\
% Visualization For Scientific Data \\
% \sectionsep

% \subsection{Undergraduate}

% Database Management Systems \textbullet{}\\
% Object Oriented Analysis and Design \textbullet{}\\
% Artificial Intelligence and Expert Systems \textbullet{}\\
% Scripting Languages and Web Tech \textbullet{}\\
% Software Engineering \\

\end{minipage} 
\end{document}  \documentclass[]{article}

