
\documentclass[letterpaper,10pt]{article} % Change 'a4paper' to 'letterpaper'
\raggedright

\usepackage[left=0.75in, right=0.75in, top=0.75in, bottom=0.75in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}

\pagestyle{empty}

% Adjust section title formatting
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{4pt}{2pt}

% Define a command for the company name and job title formatting
\newcommand{\job}[3]{
\textbf{#1 - #2} \hfill \textit{#3}
}

% Define a command for the education section
\newcommand{\education}[4]{
  \textbf{#1 - #2} \hfill #3
}

% Set the page geometry
\geometry{top=0.5in, bottom=0.5in, left=0.5in, right=0.5in}

\begin{document}

\small % Set the font size to \small

\section{\centerline{\LARGE \textnormal{Taylor J Turner}}}
Email: resume.tturner@gmail.com \hfill Phone: (618) 402-4677 \hfill LinkedIn: \href{https://www.linkedin.com/in/ifTaylorthenHire}{linkedin.com/in/ifTaylorthenHire}
\bigskip

\begin{center}
\begin{minipage}{\textwidth}
\centering
Software and Electrical Controls Engineer with experience in advanced logistic applications, \\
hydraulic control systems, and chemical process instrumentation.
\end{minipage}
\end{center}
\bigskip

\section{Skills}
\noindent Highly skilled in diverse programming languages.\\
\hspace*{\fill} • C\# • Python • T-SQL • TypeScript • IEC 61131-3 Automation Standard \hspace*{\fill}

\noindent Experience with various frameworks and libraries.\\
\hspace*{\fill} • ASP.NET Core • Entity Framework • SQLAlchemy • FastAPI • gRPC • React.js • Angular \hspace*{\fill}

\noindent Proficient using development tools and environments.\\
\hspace*{\fill} • Visual Studio/Code • Git • GitHub • Azure • Vercel • Postman \hspace*{\fill} \\
\hspace*{\fill} • Studio 5000 • TwinCAT • TIA Portal • Ignition Designer • Indusoft \hspace*{\fill}

\noindent Strong background in methodologies and concepts.\\
\hspace*{\fill} • Agile/Sprint • Object-Oriented Programming (OOP) • Failure Modes and Effects Analysis (FMEA) \hspace*{\fill} \\
\hspace*{\fill} • UL 508A • SCADA • Project Management \hspace*{\fill}

\section{Work Experience}
\noindent\job{Bastian Solutions}{Software Engineer}{September 2022 -- Present}
\begin{itemize}[left=2em]
    \item Led the modernization of palletization applications by migrating legacy WinForms systems to .NET Core and React.js/Angular, improving performance and scalability across enterprise deployments.
    \item Designed and implemented Azure-based solutions for blob storage and containerized deployments, streamlining CI/CD pipelines and reducing deployment time by 40%.
    \item Developed API brokers and real-time resource managers to facilitate communication between WMS servers and peripheral devices, enhancing system responsiveness and reliability.
    \item Spearheaded the transition of R&D products to manufacturing by establishing robust integration testing frameworks and leveraging product analytics for iterative improvements.
    \item Engineered software for logistics automation, integrating with robots, vision systems, and controllers to ensure seamless warehouse operations.
    \item Developed a Python application using Dependency Injector to interface with an IFM vision system, enabling real-time pallet location detection; serialized and transmitted location data to a FANUC robot via socket server, improving pick accuracy and reducing cycle time by 15%.
\end{itemize}

\noindent\job{Beckwood Press}{Electrical Controls Engineer II}{October 2021 – September 2022}
\begin{itemize}[left=2em]
    \item Developed embedded closed-loop algorithms for output modeling and discrete kinematic control, enhancing machine precision and reliability.
    \item Designed numerical and computational methods for sensor filtering and linearization, improving data accuracy and system performance.
    \item Created databases for machine parameterization and programming, streamlining configuration and reducing setup time by 30%.
    \item Led machine performance studies on new product lines, providing actionable insights for market application and product improvement.
\end{itemize}

\noindent\job{Beckwood Press}{Electrical Controls Engineer I}{October 2017 – October 2021}
\begin{itemize}[left=2em]
    \item Oversaw the electrical design and program development of hydraulic processes and automation integration, enabling rapid development of custom processes and competitive integration.
    \item Developed electrical design standardization under UL 508A specification and certification, ensuring compliance and enhancing safety.
    \item Led press and machine start-up and final acceptance testing, demonstrating high-performance processes and quality designs to customers.
\end{itemize}

\noindent\job{Beckwood Press}{Electrical Controls Technician}{October 2016 – October 2017}
\begin{itemize}[left=2em]
    \item Facilitated communication between engineering and production through documentation and process management, improving workflow efficiency.
    \item Developed electrical designs and programming solutions, demonstrating decision-making responsibilities, leadership, and passion.
    \item Assisted with process and programming troubleshooting for customers, ensuring timely resolution and customer satisfaction.
\end{itemize}

\noindent\job{EPIC Inc.}{Electrical Controls Electrician}{December 2014 – October 2016}
\begin{itemize}[left=2em]
    \item Assembled and designed electrical panels and machine wiring for pilot plants, vision systems, and custom machines, ensuring compliance with sanitary/wash-down, Class I Division I, and National Electric Code requirements.
    \item Assisted engineering during start-up and final acceptance testing, ensuring successful project completion.
    \item Cross-trained in process design, enhancing versatility and skill set.
\end{itemize}

\section{Education}
\education{Ranken Technical College}{Associate Degree in Electrical Control Systems}{December 2014}

\section{Volunteer}
\job{Offensive/Defensive Line Football Coach}{Titans of Troy, IL}{}

\end{document}