
\documentclass[letterpaper,10pt]{article} % Change 'a4paper' to 'letterpaper'
\raggedright

\usepackage[left=0.75in, right=0.75in, top=0.75in, bottom=0.75in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{multicol}

\pagestyle{empty}

% Adjust section title formatting
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{4pt}{2pt}

% Define a command for the company name and job title formatting
\newcommand{\job}[3]{
\textbf{#1 - #2} \hfill \textit{#3}
}

% Define a command for the education section
\newcommand{\education}[4]{
  \textbf{#1 - #2} \hfill #3
}

% Set the page geometry
\geometry{top=0.5in, bottom=0.5in, left=0.5in, right=0.5in}

\begin{document}

\small % Set the font size to \small

\section{\centerline{\LARGE \textnormal{Taylor J Turner}}}
Email: resume.tturner@gmail.com \hfill Phone: (618) 402-4677 \hfill LinkedIn: \href{https://www.linkedin.com/in/ifTaylorthenHire}{linkedin.com/in/ifTaylorthenHire}
\bigskip

\begin{center}
\begin{minipage}{\textwidth}
\centering
Software and Electrical Controls Engineer with experience in advanced logistic applications, \\
hydraulic control systems, and chemical process instrumentation.
\end{minipage}
\end{center}
\bigskip

\section{Skills}
\noindent
\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}} p{0.2\textwidth} p{0.75\textwidth}}
\textbf{Languages:} & C\#, Python, TypeScript, T-SQL, Structured Text (IEC 61131-3) \\
\textbf{Backend:} & ASP.NET Core, FastAPI, SQLAlchemy, Entity Framework, gRPC \\
\textbf{Frontend:} & React.js, Angular, Tailwind CSS, HTML5, CSS3 \\
\textbf{DevOps / Cloud:} & Azure, Docker, GitHub Actions, Vercel, CI/CD Pipelines \\
\textbf{Tools:} & Visual Studio, VS Code, Git, Postman, Figma \\
\textbf{Automation / SCADA:} & Studio 5000, TwinCAT, TIA Portal, Ignition, Indusoft \\
\textbf{Methodologies:} & OOP, Agile/Scrum, FMEA, SCADA Design, UL 508A, Project Management \\
\end{tabular*}

\section{Work Experience}
\noindent\job{Bastian Solutions}{Software Engineer}{September 2022 -- Present}
\begin{itemize}[left=2em]
    \item Led the modernization of palletization applications by migrating legacy WinForms systems to .NET Core and React.js/Angular, improving performance and scalability across enterprise deployments.
    \item Designed and implemented Azure-based solutions for blob storage and containerized deployments, streamlining CI/CD pipelines and reducing deployment time by 40%.
    \item Developed API brokers and real-time resource managers to facilitate communication between WMS servers and peripheral devices, enhancing system responsiveness and reliability.
    \item Spearheaded the transition of R&D products to manufacturing by establishing robust integration testing frameworks and leveraging product analytics for iterative improvements.
    \item Engineered software for logistics automation, integrating with robots, vision systems, and controllers to ensure seamless warehouse operations.
    \item Developed a Python application using Dependency Injector to interface with an IFM vision system, enabling real-time pallet location detection; serialized and transmitted location data to a FANUC robot via socket server, improving pick accuracy and reducing cycle time by 15%.
\end{itemize}

\noindent\job{Electrical Controls Engineer II}{Beckwood Press}{October 2021 – September 2022}
\begin{itemize}[left=2em]
    \item Developed embedded closed-loop algorithms for output modeling and discrete kinematic control.
    \item Designed numerical and computational methods for sensor filtering and linearization.
    \item Created databases for machine parameterization and programming.
    \item Led machine performance studies on new product lines for application in the marketplace.
\end{itemize}

\noindent\job{Electrical Controls Engineer I}{Beckwood Press}{October 2017 – October 2021}
\begin{itemize}[left=2em]
    \item Oversaw the electrical design and program development of hydraulic processes and automation integration. Custom electrical and programming structure allowed rapid development of custom processes and competitive integration.
    \item Developed electrical design standardization under UL 508A specification and certification.
    \item Led press and machine start up and final acceptance testing. It is rewarding to demonstrate high performance processes and quality designs to customers.
\end{itemize}

\noindent\job{Electrical Controls Technician}{Beckwood Press}{October 2016 – October 2017}
\begin{itemize}[left=2em]
    \item Facilitated communication between engineering and production through documentation and process management.
    \item Began developing electrical designs and programming solutions. Growth within the organization allowed me to demonstrate decision making responsibilities, leadership, and a passion.
    \item Assisted with process and programming troubleshooting for customers.
\end{itemize}

\noindent\job{Electrical Controls Electrician}{EPIC Inc.}{December 2014 – October 2016}
\begin{itemize}[left=2em]
    \item Assembled and designed electrical panels and machine wiring for pilot plants, vision systems, and custom machines.
    \item Implemented designs conforming to sanitary/wash-down, Class I Division I, and National Electric Code requirements.
    \item Assisted engineering during start-up and final acceptance testing.
    \item Cross-trained in process design.
\end{itemize}

\section{Education}
\education{Ranken Technical College}{Associate Degree in Electrical Control Systems}{December 2014}

\section{Volunteer}
\job{Offensive/Defensive Line Football Coach}{Titans of Troy, IL}{}

\end{document}