\documentclass[letterpaper,10pt]{article} % Change 'a4paper' to 'letterpaper'

\usepackage[left=0.75in, right=0.75in, top=0.75in, bottom=0.75in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}

\pagestyle{empty}

% Adjust section title formatting
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{4pt}{2pt}

% Define a command for the company name and job title formatting
\newcommand{\job}[3]{
\textbf{#1 - #2} \hfill \textit{#3}
}

% Define a command for the education section
\newcommand{\education}[4]{
  \textbf{#1 - #2} \hfill #3
}

% Set the page geometry
\geometry{top=0.5in, bottom=0.5in, left=0.5in, right=0.5in}

\begin{document}

\small % Set the font size to \small

\section{\centerline{\LARGE \textnormal{Taylor J Turner}}}
Email: resume.tturner@gmail.com \hfill Phone: (618) 402-4677 \hfill LinkedIn: \href{https://www.linkedin.com/in/ifTaylorthenHire}{linkedin.com/in/ifTaylorthenHire}
\bigskip

\section{Summary}
Software / Electrical Controls Engineer with extensive experience leading technical projects and developing innovative software solutions.

\section{Skills}
\noindent Highly skilled in diverse programming languages.\\
\hspace*{\fill} • C\# • Python • T-SQL • TypeScript • IEC 61131-3 Automation Standard \hspace*{\fill}

\noindent Experience with various frameworks and libraries.\\
\hspace*{\fill} • ASP.NET Core • Entity Framework • T-SQL • Flask • gRPC • React.js \hspace*{\fill}

\noindent Proficient using development tools and environments.\\
\hspace*{\fill} • Visual Studio/Code • Git • Github • Azure • Vercel • Postman \hspace*{\fill} \\
\hspace*{\fill} • Studio 5000 • TwinCAT • TIA Portal • Ignition Designer • Indusoft \hspace*{\fill}

\noindent Strong background in methodologies and concepts.\\
\hspace*{\fill} • Agile/Sprint • Object-Oriented Programming (OOP) • Failure Modes and Effects Analysis (FMEA) \hspace*{\fill} \\
\hspace*{\fill} • UL 508A • SCADA • Project Management \hspace*{\fill}


\section{Work Experience}
\noindent\job{Bastian Solutions}{Software Engineer}{September 2022 -- Present}
\begin{itemize}[left=2em]
	\item Developed software for manufacturing applications and interfacing automation controllers, robots, and vision systems.
	\item Migrated palletization applications from WinForms to .NET Core and Next.js/React.js frameworks.
	\item Created python/C+ clients to support warehouse management systems' communication with peripheral. The integration of this software required threaded processes, real-time resource locking, and micro-controller-controlled HID interfaces.
	\item Enhanced robot picking applications to bridge device communication using Python.
	\item Transitioned products from R\&D to manufacturing, focusing on continuous improvement in integration testing and product statistics.
\end{itemize}

\noindent\job{Electrical Controls Engineer II}{Beckwood Press}{October 2021 – September 2022}
\begin{itemize}[left=2em]
	\item Designed numerical and computational methods for sensor filtering and linearization.
	\item Developed embedded closed-loop algorithms for output modeling and discrete kinematic control.
	\item Created databases for machine parameterization and programming.
	\item Led machine performance studies on new product lines for application in the marketplace.
\end{itemize}

\noindent\job{Electrical Controls Engineer I}{Beckwood Press}{October 2017 – October 2021}
\begin{itemize}[left=2em]
	\item Oversaw the electrical design and program development of hydraulic processes and automation integration. Custom design
	structure allowed rapid development of custom processes and competitive integration.
	\item Developed electrical design standardization under UL 508A specification and certification.
	\item Led press and machine start up and final acceptance testing. It is rewarding to demonstrate high performance process
	quality and understanding to customers.
\end{itemize}
	
\noindent\job{Electrical Controls Technician}{Beckwood Press}{October 2016 – October 2017}
\begin{itemize}[left=2em]
	\item Facilitated communication between engineering and production through documentation and process management.
	\item Began developing electrical designs and programing solutions. Growth within the organization allowed me to demonstrate
	decision making responsibilities, leadership, and a passion.
	\item Assisted with process and programming troubleshooting for customers.
\end{itemize}

\noindent\job{Electrical Controls Electrician}{EPIC Inc.}{December 2014 – October 2016}
\begin{itemize}[left=2em]
	\item Assembled and designed electrical panels and machine wiring for pilot plants, vision systems, and custom machines.
	\item Implemented designs conforming to sanitary/wash-down, Class I Division I, and National Electric Code requirements.
	\item Assisted engineering during start-up and final acceptance testing.
	\item Cross-trained in process design.
\end{itemize}

\section{Education}
\education{Ranken Technical College}{Associate Degree in Electrical Control Systems}{December 2014}

\section{Volunteer}
\job{Offensive/Defensive Line Coach}{Titans of Troy, IL}{}


\end{document}
